---
title: "p8510_hw1"
author: "joseph Kim"
date: "9/29/2021"
output: github_document
---

## Problem 1

##### Create a data frame comprised of:

- a random sample of size 10 from a standard Normal distribution
- a logical vector indicating whether elements of the sample are greater than 0
- a character vector of length 10
- a factor vector of length 10, with 3 different factor “levels”


```{r, message=F}

library(tidyverse)

dataframe_1 = tibble(
  vec_numeric = rnorm(10, sd=1),
  vec_logical = vec_numeric > 0, 
  vec_char = c("Boy", "Girl", "Tent", "Camp", "Bee", "Dog", "Cat", "Lion", "Ben", "Pool"),
  vec_factor = factor(c("First", "Second", "Third", "Third", "First", "First", "Second", "Second", "Third", "First")
  )
)

```

--------------

##### 1B) Try to take the mean of each variable in your dataframe. What works and what doesn’t?

```{r}
##### Checking Means of each variable ###

library(tidyverse)
mean(dataframe_1$vec_numeric)
mean(dataframe_1$vec_logical)
mean(dataframe_1$vec_char)
mean(dataframe_1$vec_factor)
```

You can not take the mean of the vec_char and vec_factor because they are not numerical values. 


