---
title: "p8510_hw1"
author: "joseph Kim"
date: "9/29/2021"
output: github_document
---

## Problem 1

###### Create a data frame comprised of:

- a random sample of size 10 from a standard Normal distribution
- a logical vector indicating whether elements of the sample are greater than 0
- a character vector of length 10
- a factor vector of length 10, with 3 different factor “levels”


```{r, message=F}

library(tidyverse)

dataframe_1 = tibble(
  vec_numeric = rnorm(10, sd=1),
  vec_logical = vec_numeric > 0, 
  vec_char = c("Boy", "Girl", "Tent", "Camp", "Bee", "Dog", "Cat", "Lion", "Ben", "Pool"),
  vec_factor = factor(c("First", "Second", "Third", "Third", "First", "First", "Second", "Second", "Third", "First")
  )
)

```

--------------

##### 1b) Try to take the mean of each variable in your dataframe. What works and what doesn’t?

```{r}
##### Checking Means of each variable 

library(tidyverse)
mean(dataframe_1$vec_numeric)
mean(dataframe_1$vec_logical)
mean(dataframe_1$vec_char)
mean(dataframe_1$vec_factor)
```

##### You can not take the mean of the vec_char and vec_factor because they are not numerical values. 

----------

##### 1c) In some cases, you can explicitly convert variables from one type to another. Write a code chunk that applies the as.numeric function to the logical, character, and factor variables (please show this chunk but not the output). What happens, and why? Does this help explain what happens when you try to take the mean?

```{r}
### Coercing variable types 
as.numeric(dataframe_1$vec_logical)
as.numeric(dataframe_1$vec_char)
as.numeric(dataframe_1$vec_factor)

```

###### By converting variables to be numeric, it converts reoccuring values are numbers values. The vec_factor values are converted into 1,2, and 3. If we are to pull the means now, they would result in a numerical mean. 
  
------------

## Problem 2 

##### 1a) Loading Penguins Dataset 

```{r}
data("penguins", package = "palmerpenguins")

nrow(penguins)
ncol(penguins)
mean(na.omit(penguins$flipper_length_mm))
```

This dataset tells us information about certain penguins, presumably by an individual named Palmer. We are given the species, the name of the island, bill length (mm), bill depth (mm), flipper length (mm), body mass (grams), sex, and year.. The dataset consists of 344 rows and 8 columns. The mean flipper length was 200.9152 mm. 

```{r}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()

ggsave("penguins.png")
```
